\def \aap{A\&A}
\def \aaps{A\&AS}
\def \ag{Astron. Geophys.}
\def \aj{AJ}
\def \ajp{Am. J. Phys.}
\def \al{Astron. Lett.}
\def \ap{Appl. Phys.}
\def \apj{ApJ}
\def \apjl{ApJ}
\def \apjl{ApJ Lett.}
\def \apjs{ApJS}
\def \apss{Astrophys. and Space Science}
\def \araa{ARA\&A}
\def \arns{Annu. Rev. Nuc. Sci.}
\def \asp{Astron. Soc. Pac.}
\def \azh{Astronomicheskii Zhurnal}
\def \baas{BAAS}
\def \baps{Bull. Am. Phys. Soc.}
\def \bist{Bull. Inf. Sci. Tech.}
\def \ca{Comments on Astrophys.}
\def \cqg{Class. Quantum Gravity}
\def \epjc{Euro. Phys. J. C}
\def \grg{Gen. Relativ. Gravitation}
\def \ijmpd{Int. J. Mod. Phys. D}
\def \jhep{J. High Energy Phys.}
\def \jms{J. Molecular Spectrosc.}
\def \jos{J. Opt. Soc. Am.}
\def \jcap{J. Cosmo. Astropart. Phys.}
\def \josb{J. Opt. Soc. Am. B}
\def \jpcrd{J. Phys. Chem. Ref. Data}
\def \jpcrds{J. Phys. Chem. Ref. Data Suppl.}
\def \jqsrt{J. Quant. Spectrosc. Radiat. Transfer}
\def \jtp{J. Technical Phys.}
\def \met{Metrologia}
\def \mnras{MNRAS}
\def \mpla{Mod. Phys. Lett. A}
\def \nat{Nature}
\def \nature{Nature}
\def \npb{Nucl. Phys. B}
\def \nsrds{Natl. Stand. Rel. Data Ser.}
\def \nw{Naturwiss.}
\def \pasa{Publ. Astron. Soc. Austral.}
\def \pasp{PASP}
\def \pawk{Preuss. Akad. Wiss. K}
\def \plb{Phys. Lett. B}
\def \phd{PhD thesis}
\def \physrep{Physics Reports}
\def \pr{Phys. Rev.}
\def \pra{Phys. Rev. A}
\def \prb{Phys. Rev. B}
\def \prc{Phys. Rev. C}
\def \prd{Phys. Rev. D}
\def \prep{in preparation}
\def \prl{Phys. Rev. Lett.}
\def \prsa{Proc. R. Soc. A}
\def \psc{Phys. Scr.}
\def \ptp{Progress Theor. Phys.}
\def \ptrsla{Phil. Trans. R. Soc. London}
\def \qjras{Quart. J. R. Astron. Soc.}
\def \rmp{Rev. Mod. Phys.}
\def \rpp{Rep. Prog. Phys.}
\def \sovast{Soviet Astronomy}
\def \spu{Sov. Phys. Uspekhi}
\def \ssr{Space Sci. Rev.}
\def \tms{Trans. Math. Software}


\def \cup{Cambridge U. Press}
\def \cupadr{Cambridge U.K.}
\def \pup{Princeton U. Press}
\def \pupadr{Princeton, U.S.A.}

\def \etal{et al.}
